---
title: CURI Banks Data Analysis
author: Henry Fisher
output: 
  pdf_document:
    fig_height: 3.5
    fig_width: 7
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE}
library(stargazer)
library(tidyverse)
```


```{r, include = FALSE}
#Import Dataset
outcomes_0 <- read_csv("~/CURI 2023/CURI_outcomes_1.csv")
```


```{r, include = FALSE}
#Data Cleaning
outcomes <- outcomes_0 %>%
  rename(repetition = repition,
         shortfall_j = shorfall_j) %>%
  #shortfall boolean values are reversed
  mutate(shortfall_i = if_else(shortfall_i == FALSE, 1, 0),
         shortfall_j = if_else(shortfall_j == FALSE, 1, 0),
         delta_total_shortfall_dollars = new_total_shortfall_dollars - old_total_shortfall_dollars,
         delta_delinquent_count = new_delinquent_count - old_delinquent_count,
         delta_shortfall_loan_count = new_shortfall_loan_count - old_shortfall_loan_count) %>%
  select(2,4,3,5:10,14,12,15:21)
```

**Total Shortfall (Models 1-3)**

Model 1 (Total Shortfall, bank_i = bank_k) $y_i = \beta_1 + \beta_2 A_k + \beta_3 in-degree_k + \beta_4 out-degree_k + \epsilon_i$
```{r}
total.shortfall.i.lm <- lm(delta_total_shortfall_dollars ~ A_i + in_deg_i + out_deg_i, outcomes)
summary(total.shortfall.i.lm)
```

```{r, include=FALSE}
stargazer(total.shortfall.i.lm)
```


Model 2 (Total Shortfall, bank_j) $y_i = \beta_1 + \beta_2 A_j + \beta_3 in-degree_j + \beta_4 out-degree_j + \epsilon_i$
```{r}
total.shortfall.j.lm <- lm(delta_total_shortfall_dollars ~ A_j + in_deg_j + out_deg_j, outcomes)
summary(total.shortfall.j.lm)
```

```{r, include = FALSE}
stargazer(total.shortfall.j.lm)
```


Model 3 (Total Shortfall, both i and j) $y_i = \beta_1 + \beta_2 A_k + \beta_3 A_j + \beta_4 in-degree_k + \beta_5 in-degree_j + \beta_6 out-degree_k + \beta_7 out-degree_j + \epsilon_i$
```{r}
total.shortfall.lm <- lm(delta_total_shortfall_dollars ~ A_i + A_j + in_deg_i + in_deg_j + out_deg_i + out_deg_j, outcomes)
summary(total.shortfall.lm)
```

```{r, include = FALSE}
stargazer(total.shortfall.lm)
```


##Total Loans with Shortfall (Models 4-6)##

Model 4 (Loans with Shortfall, bank_i = bank_k) $y_i = \beta_1 + \beta_2 A_k + \beta_3 in-degree_k + \beta_4 out-degree_k + \epsilon_i$
```{r}
total.loans.i.lm <- lm(delta_shortfall_loan_count ~ A_i + in_deg_i + out_deg_i, outcomes)
summary(total.loans.i.lm)
```

```{r, include = FALSE}
stargazer(total.loans.i.lm)
```

Model 5 (Loans with Shortfall, bank_i = bank_k) $y_i = \beta_1 + \beta_2 A_j + \beta_3 in-degree_j + \beta_4 out-degree_j + \epsilon_i$
```{r}
total.loans.j.lm <- lm(delta_shortfall_loan_count ~ A_j + in_deg_j + out_deg_j, outcomes)
summary(total.loans.j.lm)
```

```{r, include = FALSE}
stargazer(total.loans.j.lm)
```

Model 6 (Loans with Shortfall,, both i and j) $y_i = \beta_1 + \beta_2 A_k + \beta_3 A_j + \beta_4 in-degree_k + \beta_5 in-degree_j + \beta_6 out-degree_k + \beta_7 out-degree_j + \epsilon_i$
```{r}
total.loans.lm <- lm(delta_shortfall_loan_count ~ A_i + A_j + in_deg_i + in_deg_j + out_deg_i + out_deg_j, outcomes)
summary(total.loans.lm)
```

```{r, include = FALSE}
stargazer(total.loans.lm)
```

\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
\cline{2-2} 
\\[-1.8ex] & delta\_total\_shortfall\_dollars \\ 
\hline \\[-1.8ex] 
 A\_i & $-$0.760 \\ 
  & (0.919) \\ 
  & \\ 
 in\_deg\_i & $-$13.833$^{***}$ \\ 
  & (0.983) \\ 
  & \\ 
 out\_deg\_i & 15.716$^{***}$ \\ 
  & (1.015) \\ 
  & \\ 
 Constant & 3.934 \\ 
  & (13.936) \\ 
  & \\ 
\hline \\[-1.8ex] 
Observations & 2,000 \\ 
R$^{2}$ & 0.110 \\ 
Adjusted R$^{2}$ & 0.109 \\ 
Residual Std. Error & 206.733 (df = 1996) \\ 
F Statistic & 82.356$^{***}$ (df = 3; 1996) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}


\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
\cline{2-2} 
\\[-1.8ex] & delta\_total\_shortfall\_dollars \\ 
\hline \\[-1.8ex] 
 A\_j & 1.281 \\ 
  & (0.892) \\ 
  & \\ 
 in\_deg\_j & 18.314$^{***}$ \\ 
  & (1.011) \\ 
  & \\ 
 out\_deg\_j & $-$20.364$^{***}$ \\ 
  & (0.986) \\ 
  & \\ 
 Constant & 70.606$^{***}$ \\ 
  & (12.881) \\ 
  & \\ 
\hline \\[-1.8ex] 
Observations & 2,000 \\ 
R$^{2}$ & 0.177 \\ 
Adjusted R$^{2}$ & 0.176 \\ 
Residual Std. Error & 198.804 (df = 1996) \\ 
F Statistic & 143.188$^{***}$ (df = 3; 1996) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 



\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
\cline{2-2} 
\\[-1.8ex] & delta\_total\_shortfall\_dollars \\ 
\hline \\[-1.8ex] 
 A\_i & $-$0.946 \\ 
  & (0.818) \\ 
  & \\ 
 A\_j & 1.317 \\ 
  & (0.825) \\ 
  & \\ 
 in\_deg\_i & $-$14.563$^{***}$ \\ 
  & (0.876) \\ 
  & \\ 
 in\_deg\_j & 18.866$^{***}$ \\ 
  & (0.936) \\ 
  & \\ 
 out\_deg\_i & 16.289$^{***}$ \\ 
  & (0.904) \\ 
  & \\ 
 out\_deg\_j & $-$20.886$^{***}$ \\ 
  & (0.913) \\ 
  & \\ 
 Constant & 42.891$^{**}$ \\ 
  & (17.055) \\ 
  & \\ 
\hline \\[-1.8ex] 
Observations & 2,000 \\ 
R$^{2}$ & 0.296 \\ 
Adjusted R$^{2}$ & 0.294 \\ 
Residual Std. Error & 183.966 (df = 1993) \\ 
F Statistic & 139.934$^{***}$ (df = 6; 1993) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 




\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
\cline{2-2} 
\\[-1.8ex] & delta\_shortfall\_loan\_count \\ 
\hline \\[-1.8ex] 
 A\_i & 0.017 \\ 
  & (0.033) \\ 
  & \\ 
 in\_deg\_i & 0.028 \\ 
  & (0.036) \\ 
  & \\ 
 out\_deg\_i & $-$0.013 \\ 
  & (0.037) \\ 
  & \\ 
 Constant & 0.565 \\ 
  & (0.506) \\ 
  & \\ 
\hline \\[-1.8ex] 
Observations & 2,000 \\ 
R$^{2}$ & 0.001 \\ 
Adjusted R$^{2}$ & $-$0.001 \\ 
Residual Std. Error & 7.504 (df = 1996) \\ 
F Statistic & 0.355 (df = 3; 1996) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 



\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
\cline{2-2} 
\\[-1.8ex] & delta\_shortfall\_loan\_count \\ 
\hline \\[-1.8ex] 
 A\_j & 0.018 \\ 
  & (0.034) \\ 
  & \\ 
 in\_deg\_j & 0.026 \\ 
  & (0.038) \\ 
  & \\ 
 out\_deg\_j & $-$0.022 \\ 
  & (0.037) \\ 
  & \\ 
 Constant & 0.710 \\ 
  & (0.486) \\ 
  & \\ 
\hline \\[-1.8ex] 
Observations & 2,000 \\ 
R$^{2}$ & 0.0004 \\ 
Adjusted R$^{2}$ & $-$0.001 \\ 
Residual Std. Error & 7.505 (df = 1996) \\ 
F Statistic & 0.245 (df = 3; 1996) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 




\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
\cline{2-2} 
\\[-1.8ex] & delta\_shortfall\_loan\_count \\ 
\hline \\[-1.8ex] 
 A\_i & 0.017 \\ 
  & (0.033) \\ 
  & \\ 
 A\_j & 0.019 \\ 
  & (0.034) \\ 
  & \\ 
 in\_deg\_i & 0.028 \\ 
  & (0.036) \\ 
  & \\ 
 in\_deg\_j & 0.026 \\ 
  & (0.038) \\ 
  & \\ 
 out\_deg\_i & $-$0.012 \\ 
  & (0.037) \\ 
  & \\ 
 out\_deg\_j & $-$0.020 \\ 
  & (0.037) \\ 
  & \\ 
 Constant & 0.310 \\ 
  & (0.696) \\ 
  & \\ 
\hline \\[-1.8ex] 
Observations & 2,000 \\ 
R$^{2}$ & 0.001 \\ 
Adjusted R$^{2}$ & $-$0.002 \\ 
Residual Std. Error & 7.508 (df = 1993) \\ 
F Statistic & 0.301 (df = 6; 1993) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 
